---
output: 
  html_document:
    theme: cerulean
    highlight: default
---

```{r, include=FALSE}

 
library(tidyverse)
library(AER)
library(kableExtra)
library(knitr)
source(".../data.R")
```


```{r, include=FALSE}
hooks = knitr::knit_hooks$get()

force("output")

hook_foldable <- function(x, options) {
  
    res = hooks[["output"]](x, options)
    
    if (isFALSE(options[[paste0("fold.", "output")]])) return(res)
    
    paste0(
      "<details><summary>Details</summary>\n\n",
      res,
      "\n\n</details>"
    )
}

knitr::knit_hooks$set(output = hook_foldable)

make_kable <- function(tbl){
  
  kable(tbl) %>% 
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                  full_width = F,
                  position = "left")
}


print_lm <- function(dep, reg, full){
  
    dep = paste0(dep," ~ ")
    linmod <- summary(lm(as.formula(paste(dep,reg)), full))
    make_kable(linmod$coefficients) 
}

print_probit <- function(dep, reg, full){
  
  dep = paste0("factor(", dep,") ~ ")
  probmod = summary(glm(as.formula(paste(dep,reg)),data = full, family = binomial(link = "probit")))
  
  make_kable(probmod$coefficients)
}

print_iv <- function(dep, reg, instr, controls, full){
  
  reg1 <- paste0(dep, " ~ ", reg, " + ", controls, " | ", instr, " + ", controls)
  reg2 <- paste0(reg, " ~ ", instr, " + ", controls)
  
  iv <- summary(ivreg(reg1, data = full), diagnostics = T)
  lin <- summary(lm(reg2, data = full))
  
  a = make_kable(iv$coefficients)
  b = make_kable(iv$diagnostics[-3,])
  c = make_kable(lin$coefficients)
  
  return(list(coefs = a, diags = b, fstg = c))
}
```

# {.tabset}

```{r, include=FALSE}
full_dict = read_csv(".../dict.csv") 
full <- read_csv("endvalsext.csv")
blc_full <- get_balanced_table(full)
```

## Data and Parameters

### Parameters

```{r, echo=FALSE, fold.output=FALSE}
dict <- full_dict %>% filter(family == "param")
dict <- dict[,1:2]
names(dict) <- c("Parameter", "Description")

make_kable(dict)
```

### Endogenous Variables

```{r, echo=FALSE, fold.output=FALSE}
dict <- full_dict %>% filter(family == "endog")
dict <- dict[,1:2]
dict$name <- sapply(dict$name, function(x){gsub("_mean","",x)})
names(dict) <- c("Variable", "Description")

make_kable(dict)
```

### Data

```{r, echo = FALSE, fold.output=FALSE}
make_kable(head(full,2000)) %>% 
  scroll_box(width = "100%", height = "300px")
```
$~$
```{r, echo = FALSE}
Hmisc::describe(full)
```

## Linear Models

$v_{i,r} = s^f_{i} + \delta_{i} + \lambda_{i} + \epsilon{i,r}$ 

### Incomes

#### Farmers

```{r, echo = FALSE, fold.output=FALSE}
reg = "foragers_income + prod_advantage + perc_non_farmers + prop_bandits"

print_lm("farmers_avg_income", reg, full)
```

#### Bandits

```{r, echo = FALSE, fold.output=FALSE}
print_lm("bandits_avg_income", reg, full)
```

#### Population

```{r, echo = FALSE, fold.output=FALSE}
print_lm("pop_avg_income", reg, full)
```

#### Difference Between Farmers and Bandits

```{r, echo = FALSE, fold.output=FALSE}
print_lm("diff_incomes", reg, full)
```

### Bandits Population

```{r, echo = FALSE, fold.output=FALSE}
print_lm("n_bandits", reg, full)
```

### Beta

```{r, echo = FALSE, fold.output=FALSE}
print_lm("beta", reg, full)
```

### Rates

#### Confiscation Rate
```{r, echo = FALSE, fold.output=FALSE}
print_lm("rate", reg, full)
```

#### Proposed Rate

```{r, echo = FALSE, fold.output=FALSE}
print_lm("proposed_rate", reg, full)
```

### Security Tax

```{r, echo = FALSE, fold.output=FALSE}
print_lm("security_tax", reg, full)
```

### Time to reach Hierarchy

```{r, echo = FALSE, fold.output=FALSE}
print_lm("time_to_hierarchy", reg, filter(full, time_to_hierarchy != 101))
```

## Probabilistic Models

Dependent variable: `association_level`

### Probit

```{r, echo=FALSE, fold.output=FALSE}
print_probit("association_level", reg, blc_full)
```

### Linear Probability

```{r, echo=FALSE, fold.output=FALSE}
print_lm("association_level", reg, blc_full)
```

## Causal Models

### Dependent variable: `pop_avg_income`

#### OLS

Without Controls

```{r, echo=FALSE, fold.output=FALSE}
reg = "association_level"
print_lm("pop_avg_income", reg, full)
```

With Controls

```{r, echo=FALSE, fold.output=FALSE}
reg = "association_level + foragers_income + perc_non_farmers + prop_bandits"
print_lm("pop_avg_income", reg, full)
```

```{r, echo=FALSE, fold.output=FALSE}
reg = "association_level + prod_advantage + foragers_income + perc_non_farmers + prop_bandits"
print_lm("pop_avg_income", reg, full)
```

#### 2SLS

Coeficients

```{r, echo=FALSE, fold.output=FALSE}
reg = "association_level"
instr = "prod_advantage"
controls = "foragers_income + perc_non_farmers + prop_bandits" 
tabs = print_iv("pop_avg_income", reg, instr, controls, full)

tabs$coefs
```

Diagnostics

```{r, echo=FALSE, fold.output=FALSE}
tabs$diags
```

First Stage

```{r, echo=FALSE, fold.output=FALSE}
tabs$fstg
```

### Dependent variable: `diff_incomes`

#### OLS

Without Controls

```{r, echo=FALSE, fold.output=FALSE}
reg = "association_level"
print_lm("pop_avg_income", reg, full)
```

With Controls

```{r, echo=FALSE, fold.output=FALSE}
reg = "association_level + foragers_income + perc_non_farmers + prop_bandits"
print_lm("pop_avg_income", reg, full)
```

```{r, echo=FALSE, fold.output=FALSE}
reg = "association_level + prod_advantage + foragers_income + perc_non_farmers + prop_bandits"
print_lm("pop_avg_income", reg, full)
```

#### 2SLS

Coeficients

```{r, echo=FALSE, fold.output=FALSE}
reg = "association_level"
instr = "prod_advantage"
controls = "foragers_income + perc_non_farmers + prop_bandits" 
tabs = print_iv("pop_avg_income", reg, instr, controls, full)

tabs$coefs
```

Diagnostics

```{r, echo=FALSE, fold.output=FALSE}
tabs$diags
```

First Stage

```{r, echo=FALSE, fold.output=FALSE}
tabs$fstg
```